`r params$title`

### 2019-09-02 Rmd/summary_db_cols_norman.Rmd
added cbind_fill()

```{r echo=FALSE, message=FALSE}
# schema = 'norman'
# table = 'data2_newest'
# cols = c('nor88test', 'nor88')

@@

```{r write, echo=FALSE, message=FALSE}
unlink(dir, recursive = TRUE)
mkdirs(dir)
for (i in seq_along(l)) {
  dat = l[[i]]
  nam = names(l)[i]
  fl = file.path(dir, paste0(nam, '.csv'))

@@

>>>>

```{r echo=FALSE, message=FALSE}
# schema = 'norman'
# table = 'data2_newest'
# cols = c('nor85', 'nor88')

@@

```{r write, echo=FALSE, message=FALSE}
# write summary to multiple csv
unlink(dir, recursive = TRUE)
mkdirs(dir)
for (i in seq_along(l)) {
  dat = l[[i]]
  nam = names(l)[i]
  fl = file.path(dir, paste0(nam, '.csv'))

@@

```{r write-single-file, message=FALSE}
# write summary to single file
dat = cbind_fill(dflist = l, limit = NULL)
names(dat)[ seq(1, length(names(dat)), 2) + 1 ] = paste0(names(dat)[ seq(1, length(names(dat)), 2) ], '_n')

fwrite(dat, file.path(params$output_dir, paste0(params$table, '_summary.csv')))
```
